\documentclass[14pt,letterpaper]{article}

\newcommand{\IncludePath}{../include}
\input{\IncludePath/hmwk-template.tex}

\title{Angles II}
\author{Name: \underline{\hspace{5cm}}}
\date{October 8, 2016}

\begin{document}
\HomeworkTitle

\thispagestyle{empty}

\begin{problem}{Unit Conversion}
  Recall that one turn is \SI{360}{\degree}. What is \(\frac{4}{9}\) of a turn
  in degrees? \hfill \blankE \si{\degree}
\end{problem}

\begin{problem}{Angle Sum of a Triangle I}
 Could each of the following triplets form the angles of a valid triangle?

 \begin{itemize}
  \item \SI{110}{\degree}, \SI{36}{\degree}, \SI{8}{\degree}
  \hfill Yes~~No
  \item \SI{100}{\degree}, \SI{53}{\degree}, \SI{27}{\degree}
  \hfill Yes~~No
  \item \SI{108}{\degree}, \SI{16}{\degree}, \SI{150}{\degree}
  \hfill Yes~~No
 \end{itemize}
\end{problem}

\begin{problem}{Angle Sum of a Triangle II}
 For each of the following statements, indicate whether the statement is
 possible or otherwise.

 \begin{itemize}
  \item A triangle has two obtuse angles.
  \hfill Possible~~Not Possible
  \item A triangle has three acute angles.
  \hfill Possible~~Not Possible
 \end{itemize}
\end{problem}

\begin{problem}{Angle Sum of a Triangle III}
 Find the missing angle in each triangle angle triplet.

 \begin{itemize}
  \item \SI{85}{\degree}, \SI{85}{\degree},
  \blankC \si{\degree}
  \item \SI{30}{\degree}, \SI{60}{\degree},
  \blankC \si{\degree}
  \item \SI{90}{\degree}, \SI{45}{\degree},
  \blankC \si{\degree}
 \end{itemize}
\end{problem}

\begin{problem}{Angle Sum of a Polygon}
 What is the sum of the interior angles of each following polygon?

 \begin{itemize}
  \item Hexagon ($6$-sided)
  \hfill Sum: \blankC \si{\degree}
  \item Hendecagon ($11$-sided)
  \hfill Sum: \blankC \si{\degree}
 \end{itemize}
\end{problem}

\begin{problem}{Hexagon}
 Can five of the six angles of a hexagon measure \SI{30}{\degree},
 \SI{40}{\degree}, \SI{50}{\degree}, \SI{60}{\degree}, and \SI{70}{\degree}?
\end{problem}

\begin{problem}{Challenge I}
 A \emph{convex} polygon has no reflex angles; that is, all angles of a convex
 polygon are less than \SI{180}{\degree}. Answer the below in the space
 provided.

 \begin{itemize}
  \item \SI{20}{\degree}, \SI{50}{\degree}, and \SI{110}{\degree} are the three
  interior angles of a convex triangle. What is the sum of the exterior angles
  of this triangle?
  \item Pick three other angles that add up to \SI{180}{\degree} and find the
  sum of exterior angles of the triangle that contains those angles. What do you
  notice?
  \item What is the sum of the exterior angles of a convex polygon? Hint: Pick
  $5$ angles that sum to \SI{540}{\degree}. Calculate the exterior angles and
  add those up.
  \item What is true about the sum of exterior angles of any polygon? Why do you
  think this is the case?
 \end{itemize}
\end{problem}

\begin{problem}{Challenge II}
  An \emph{equiangular} polygon is a polygon whose angles are all equal. There
  is a number $n$ with the property that in an $n$-sided equiangular polygon,
  all the angles measure \SI{175}{\degree}. What is $n$?
\end{problem}

\end{document}
