\documentclass[a4paper,10pt]{report}

\newcommand{\IncludePath}{../include}
\newcommand{\ProjectName}{Grade 4 Olympic Math}
\input{\IncludePath/book-template.tex}

% use glossaries for this document
\input{\IncludePath/gloss-g4.tex}
\makeglossaries

\title{Discrete Mathematics}
\author{Fengyang Wang}
\date{November 26, 2016}

\begin{document}

\begin{abstract}

This is a rough sketch of lessons in discrete mathematics suitable for an
advanced Grade 4 audience. These notes were prepared for the Grand River
Chinese School. Each chapter may take two to four hours to deliver entirely,
depending on the level of detail.

These notes are intended to be a very rough outline of what is taught, and not
a rigorous and complete reference. I do not necessarily cover all the material
written in these notes in any particular year, and I may occasionally cover
material beyond that written in the notes.

Although the notes are intended to be presented to a young audience, they are
written for a teacher and not for a student. Many of the terms used will not be
familiar to the students, and will need to be explained differently.

\end{abstract}

\maketitle

\tableofcontents

\chapter{Collections}

\section{Pairs}

An \gls{ordered pair} is two things written in an order. For example, \((3,
4)\) is an ordered pair of numbers. Ordered pairs frequently represent a single
concept that is made of two components.

A simple ordered pair like \((3, 4)\) does not itself have much meaning, aside
from being a collection of two numbers. However, we may assign an
interpretation to particular ordered pairs to give them a meaning.

\subsection{Fractions}

\Glspl{fraction} are a common example of ordered pairs with an assigned
interpretation. The fraction \(\frac{a}{b}\) is itself an ordered pair \((a,
b)\), with the first element of this ordered pair representing the number to
divide, and the second element representing the number to be divided by.

\begin{problem}{Fractions}
 Compute each of the following:

 \[
         \frac{3}{8} \times \frac{2}{7} = \frac{6}{56} =
         \Ans{\displaystyle\frac{3}{28}}
        \]
 \[
  \frac{5}{9} \times \frac{2}{5} = \frac{10}{45} =
  \Ans{\displaystyle\frac{2}{9}}
  \]
\end{problem}

It happens to be the case with fractions that distinct ordered pairs might
represent the same quantity. For instance, \(\frac{3}{6}\) and \(\frac{7}{14}\)
are different pairs of numbers, but they represent the same fraction: one half.
All the fractions that represent a particular quantity form a so-called
\emph{equivalence class}. All numbers that can be formed from fractions of
integers are called \glspl{rational number}.

\subsection{Two-Dimensional Vector Spaces}

Another interpretation of ordered pairs is as vectors in a two-dimensional
plane. Recall from our measurement unit that the components of the vector \([a,
b]\) represent the displacement in two directions. For example, the first
component might represent displacement to the right, and the second component
displacement toward top of the page. (Such an interpretation is called a
\emph{vector space}, and the choices of directions are collectively called a
\emph{basis}.)

\section{Sets}

A set is an unordered collection of distinct objects. Topics to cover:

\begin{itemize}
  \item finite sets
  \item cardinality
  \item set operations
  \item inclusion-exclusion
  \item infinite sets
\end{itemize}

\subsection{Sets as Collections}

TK.

\subsection{Set Union}

TK.

\subsection{Set Intersection}

TK.

\subsection{To Infinity and Beyond}

TK.

\chapter{Functions of One Variable}

\section{Introduction}

Imagine a factory where raw materials are converted into finished products.
Each different kind of raw material is converted into a different kind of
product. At our factory, wood is converted into furniture, glass into windows,
silk into clothing, and cotton also into clothing. We can create a table
describing which raw materials are accepted, and which goods are produced from
those raw materials (Figure~\ref{fov:factory}).

\begin{figure}
 \renewcommand{\arraystretch}{1.2}
 \begin{tabular}{|c|c|}
  \hline
  \textbf{In} & \textbf{Out} \\
  \hline
  wood & furniture \\
  glass & windows \\
  silk & clothing \\
  cotton & clothing \\
  \hline
 \end{tabular}

 \caption{Raw inputs accepted by a factory and the outputs associated with
 them}
 \label{fov:factory}
\end{figure}

The factory that we have described is a simple example of a \gls{function}. For
each input that a function accepts, it has a particular output. The set of
possible inputs that a function accepts is called the \gls{domain} of the
function, and the set of possible outputs is called the \gls{range}. For the
function above, the domain consists of wood, glass, silk, and cotton, and the
range consists of furniture, windows, and clothing.

Another way to think about a function, then, is an object that takes any
element in its domain, and associates it with an element of the range. TK.

In mathematics, we often (but not always) deal with function that associate
numbers with numbers. For instance, the table of values in Figure~

\begin{figure}
  \renewcommand{\arraystretch}{1.2}
  \begin{tabular}{|c|c|}
    \hline
    \textbf{In} & \textbf{Out} \\
    \hline
    \(1\) & \(3\) \\
    \(2\) & \(3\) \\
    \(3\) & \(5\) \\
    \(4\) & \(4\) \\
    \hline
  \end{tabular}

  \caption{A function over the domain \(\{1, 2, 3, 4\}\)}
\end{figure}

We see examples of functions all the time in mathematics. A simple example is
the successor function, which takes each whole to the next number. This
function is TK.

\chapter{Functions of Multiple Variables}

\chapter{Recursion}

\chapter{Algorithms}

\chapter{Intuitionist Logic}

Logical thinking is the kind of reasoning necessary to make logical and correct
conclusions from givens. Much of logic can be thought of as building up
statements using rules.

\chapter{Applications}


% Glossaries and List of Figures
\printglossaries

\cleardoublepage
\addcontentsline{toc}{chapter}{\listfigurename}
\listoffigures

\end{document}
