\documentclass[12pt,letterpaper]{article}

\newcommand{\IncludePath}{../include}
\input{\IncludePath/hmwk-template.tex}

\title{Subset Sum \& Other Puzzles}
\author{Name: \underline{\hspace{5cm}}}
\date{April 23, 2016}

\begin{document}

\maketitle

\thispagestyle{empty}

Some of these puzzles might be quite hard. Get things as close to zero, or as
short, as possible. You might not find the shortest possible solution and that's
okay. We'll go over the correct answers in class.

The \textsc{Subset Sum} problem is not hard to state. We have a set of numbers;
that is, a collection of several different numbers. The question is: can we find
a nonempty subset of numbers that sums to zero? For instance, if our set is
$\{1, 2, 3\}$, then the answer is obviously no. We only have positive numbers,
so we can't possibly make $0$. But if our set is $\{-1, 1, 2\}$, then we can do
it. Take $-1 + 1 = 0$. We did not use the $2$, but that's okay. We can use any
nonempty subset---that is, we can't use no numbers, and we can't use any number
more than once.

\begin{problem}{Subset Sum I}
 Find a subset of $\{-5, 1, 2, 3, 4\}$ that sums to $0$.
\end{problem}

\begin{problem}{Subset Sum II}
 Find a subset of $\{-13, -8, 1, 2, 3, 4\}$ that sums to $0$.
\end{problem}

\begin{problem}{Subset Sum III}
 Find a subset of $\{-100, -10, 5, 15, 105, 120\}$ that sums to $0$.
\end{problem}

\begin{problem}{Subset Sum IV}
 Find a subset of $\{-390, -380, -370, -360, -352, -342, -332, -120, 2000,
 2016\}$ that sums to $0$.
\end{problem}

\vspace{2em}

HELLO is a word with five letters, and MELON is a word with five letters. The
``word'' HMELLON has just seven letters, and we can find both words (in the
right order) in it, though we need to ignore two letters in both cases. We say
that HMELLON is a \textsc{Shortest Common Supersequence} of HELLO and MELON,
because we can't do this in any fewer than $7$ letters.

\begin{problem}{Shortest Common Supersequence I}
 Find a shortest common supersequence of OLYMPIC and MATH.
\end{problem}

\begin{problem}{Shortest Common Supersequence II}
 Find a shortest common supersequence of SHORTEST and SUPERSEQUENCE.
\end{problem}

\begin{problem}{Shortest Common Supersequence III}
 Find a shortest common supersequence of the words THIS and MIGHT and BE and
 QUITE and HARD.
\end{problem}

\begin{problem}{Shortest Common Supersequence IV}
 Find a shortest common supersequence of the words IF and THAT and WAS and HARD
 and THEN and THIS and IS and HARDER.
\end{problem}

\vspace{2em}

We define the \textsc{Levenstein Distance} between two strings to be the minimum
number of edits we need to turn one string into another. One edit is either:
\begin{itemize}
 \item adding a character
 \item removing a character
 \item turning a character into another
\end{itemize}

As an example, the Levenshtein Distance between HELLO and MELON is $3$. We may,
for example, change H to M, then delete one L, and then add an N. There are
other ways of achieving the same result, but the best we can do is $3$ edits.

\begin{problem}{Levenshtein Distance I}
 Find the Levenshtein Distance between OLYMPIC and MATH.
\end{problem}

\begin{problem}{Levenshtein Distance II}
 Find the Levenshtein Distance between LEVENSHTEIN and DISTANCE.
\end{problem}

\end{document}
