\documentclass[12pt,letterpaper]{article}

\newcommand{\IncludePath}{../include}
\input{\IncludePath/hmwk-template.tex}

\title{Parity}
\author{Answers}
\date{February 27, 2016}

\begin{document}

\maketitle

\thispagestyle{empty}

\begin{problem}{Odd or even?}
For each of the following numbers, circle ``Odd'' or ``Even''.
\begin{enumerate}
 \item $17$ \hfill \AnsT{Odd} \hspace{1em} Even
 \item $49494$ \hfill Odd \hspace{1em} \AnsT{Even}
 \item $41 + 29 + 302$ \hfill Odd \hspace{1em} \AnsT{Even}
 \item $621203 - 192935$ \hfill Odd \hspace{1em} \AnsT{Even}
 \item $621203 \times 192935$ \hfill \AnsT{Odd} \hspace{1em} Even
 \item $41 \times 29 \times 302$ \hfill Odd \hspace{1em} \AnsT{Even}
\end{enumerate}
\end{problem}

\begin{problem}{Elementary School}
 At an Elementary School, there is an even number of students, an odd number of
 teachers, and $17$ other staff members. Is the total number of people in this
 school even or odd? \AnsT{Even}
\end{problem}

\begin{problem}{Fair Share}
 Without cutting any chocolates in half, can I divide $21$ chocolates fairly
 among $2$ people? \AnsT{No}
\end{problem}

\begin{problem}{Even Number}
 All even numbers are divisible by \Ans{1} and \Ans{2}.
\end{problem}

\begin{problem}{Rectangle}
 Look at the diagram below.

 \begin{center}
 \begin{tikzpicture}
  \draw[step=0.5] (0,0) grid (7,5.5);
 \end{tikzpicture}
 \end{center}

 \begin{enumerate}
  \item What are the dimensions of the rectangle? \hfill
  $\Ans{11\times14}$
  \item Is the width of the rectangle (in terms of the widths of the small
  squares) even or odd? \AnsT{Even}
  \item Is the height of the rectangle (in terms of the heights of the small
  squares) even or odd? \AnsT{Odd}
  \item Is the number of small squares even or odd? \AnsT{Even}
 \end{enumerate}
\end{problem}

\begin{problem}{Challenge}
 Recall that for any number $n$, we define $n^2$ ($n$ squared) to mean
 $n\times n$. For example, $2^2=2\times2=4$, and $10^2=10\times10=100$.

 \begin{enumerate}
  \item Calculate $1^2$, $3^2$, $5^2$, $7^2$, and $9^2$.
  \Ans{1, 9, 25, 49}
  \item Without calculating $741^2$, \emph{hypothesize} (that is, make an
  educated guess) whether it is odd or even.
  \AnsT{Odd}
  \item Use a calculator to check whether your hypothesis was correct.
  \Ans{741^2=549081}
  \item Calculate $4^2$, $6^2$, and $8^2$. \Ans{16, 36, 64}
  \item Without calculating $742^2$, hypothesize whether it is odd or even.
  \AnsT{Even}
  \item Use a calculator to check whether your hypothesis was correct.
  \Ans{742^2=550564}
  \item Hypothesize an answer for the following questions:
  When is the square of a number even? When is it odd?
  \AnsT{The square of a number is even if and only if the number is even.}
 \end{enumerate}
\end{problem}

\end{document}
