\documentclass[12pt,letterpaper]{article}

\usepackage{tikz}
\usetikzlibrary{shapes}

\usepackage{amssymb,amsmath,amsthm}
\usepackage{enumerate}
\usepackage[margin=1.25in]{geometry}
\usepackage{graphicx,ctable,booktabs}
\usepackage{fancyhdr}
\usepackage[utf8]{inputenc}

\makeatletter
\newenvironment{problem}{\@startsection
       {section}
       {1}
       {-.2em}
       {-3.5ex plus -1ex minus -.2ex}
       {2.3ex plus .2ex}
       {\pagebreak[3]
       \large\bf\noindent{Problem }
       }
       }
\makeatother

\title{Factors \& Multiples}
\author{Name: \underline{\hspace{5cm}}}
\date{February 21, 2015}

\pagestyle{fancy}
\lhead{Factors \& Multiples}
\chead{} 
\rhead{\thepage} 
\lfoot{\small\scshape Grade 4 Olympic Math} 
\cfoot{} 
\rfoot{} 
\renewcommand{\headrulewidth}{.3pt} 
\renewcommand{\footrulewidth}{.3pt}
\setlength\voffset{-0.25in}
\setlength\textheight{648pt}
\setlength\headheight{15pt}

\begin{document}

\maketitle

\thispagestyle{empty}

The symbol $\mid$ means ``divides''. If $A$ and $B$ are
two numbers, then $A$ divides $B$ when $B \div A$ has
no remainder.

A number is a \emph{factor} of another number if it divides
that number. For example, $3$ is a \emph{factor} of $9$
because $3 \mid 9$. A number is a \emph{multiple} of
another number if the other number divides it. For example,
$9$ is a \emph{multiple} of $3$.

$1$ is a \emph{factor} of every whole number, and $0$ is
a \emph{multiple} of every whole number.

\begin{problem}{Missing Entry}
Fill in the correct term in the blanks, choosing from
``divides'', ``factor'', and ``multiple''.

\begin{itemize}
 \item $3$ is a \underline{\hspace{10em}} of $12$
 \item $2$ is a \underline{\hspace{10em}} of all even
 numbers.
 \item $5$ \underline{\hspace{10em}} $100$.
 \item $100$ is a \underline{\hspace{10em}} of $5$.
 \item A number is always a \underline{\hspace{10em}} of
 itself. It's also always a \underline{\hspace{10em}} of
 itself!
\end{itemize}
\end{problem}

\begin{problem}{Multiples of $3$ and $6$}

 \begin{itemize}
  \item 
 Complete this list of multiples of $3$: 
 $0$, $3$, $6$, \underline{\hspace{2em}},
 \underline{\hspace{2em}}, \underline{\hspace{2em}},
 $18$, \ldots

 \item
 Complete this list of multiples of $6$: 
 $0$, $6$, $12$, \underline{\hspace{2em}},
 \underline{\hspace{2em}}, \underline{\hspace{2em}},
 $36$, \ldots
 \end{itemize}
\end{problem}

\begin{problem}{Rectangle 2}
 Look at the diagram below. Each small square is one square
 unit.
 
 \begin{center}
 \begin{tikzpicture}
  \draw[step=0.5] (0,0) grid (5,3.5);
 \end{tikzpicture}
 \end{center}
 
 \begin{enumerate}
  \item The rectangle has area \underline{\hspace{4em}}
  square units.
  \item $7$ is a \underline{\hspace{10em}} of the
  rectangle's area.
  \item The rectangle's area is a \underline{\hspace{10em}}
  of $10$.
 \end{enumerate}
\end{problem}

\begin{problem}{Factors of $20$}
 List all the factors of $20$:
 \underline{\hspace{2em}}, \underline{\hspace{2em}},
 \underline{\hspace{2em}}, \underline{\hspace{2em}},
 \underline{\hspace{2em}}, \underline{\hspace{2em}}
\end{problem}

\begin{problem}{Perfect Number}
 A number is \emph{perfect} if the sum of its factors is
 equal to twice the number itself. For example, $6$ is
 perfect because $1+2+3+6=12=6\times2$. Which of the
 following is a perfect number: $10$, $17$, $28$?
\end{problem}

\begin{problem}{Challenge}
 \begin{enumerate}
  \item How many factors does $1$ have?
  \item How many factors does $2$ have?
  \item How many factors does $4$ have?
  \item How many factors does $8$ have?
  \item The notation $2^{10}$ means $\underbrace{ 
  2\times2\times2\times
  \ldots\times2}_\text{$10$ twos}$; that is, $10$ twos multiplied together.
  $2^{10}=1024$. How many factors does $1024$ have?
 \end{enumerate}

\end{problem}



\end{document}