\documentclass[12pt,letterpaper]{article}

\usepackage{tikz}
\usetikzlibrary{shapes}

\usepackage{amssymb,amsmath,amsthm}
\usepackage{enumerate}
\usepackage[margin=1.25in]{geometry}
\usepackage{graphicx,ctable,booktabs}
\usepackage{fancyhdr}
\usepackage[utf8]{inputenc}

\makeatletter
\newenvironment{problem}{\@startsection
       {section}
       {1}
       {-.2em}
       {-3.5ex plus -1ex minus -.2ex}
       {2.3ex plus .2ex}
       {\pagebreak[3]
       \large\bf\noindent{Problem }
       }
       }
\makeatother

\title{Review: Prime Numbers}
\author{Name: \underline{\hspace{5cm}}}
\date{March 14, 2015}

\pagestyle{fancy}
\lhead{Review: Prime Numbers}
\chead{} 
\rhead{\thepage} 
\lfoot{\small\scshape Grade 4 Olympic Math} 
\cfoot{} 
\rfoot{}
\renewcommand{\headrulewidth}{.3pt} 
\renewcommand{\footrulewidth}{.3pt}
\setlength\voffset{-0.25in}
\setlength\textheight{648pt}
\setlength\headheight{15pt}

\begin{document}

\maketitle

\thispagestyle{empty}

A list of all prime numbers less than $100$: $2$, $3$,
$5$, $7$, $11$, $13$, $17$, $19$, $23$, $29$, $31$,
$37$, $41$, $43$, $47$, $53$, $59$, $61$, $67$,
$71$, $73$, $79$, $83$, $89$ and $97$.

\begin{problem}{Composite}
 Complete the factor pairs.
 
 \begin{itemize}
  \item $12 = 1 \times \underline{\hspace{2em}}$
  \item $12 = 2 \times \underline{\hspace{2em}}$
  \item $12 = 3 \times \underline{\hspace{2em}}$
  \item $12 = 4 \times \underline{\hspace{2em}}$
  \item $12 = 6 \times \underline{\hspace{2em}}$
  \item $12 = 12 \times \underline{\hspace{2em}}$
 \end{itemize}

\end{problem}

\begin{problem}{Prime Factor}
 Find one (no need to find all) prime factor for each number.
 
 \begin{itemize}
  \item $99959386$ \hfill Factor: \underline{\hspace{2em}}
  \item $521976505$ \hfill Factor: \underline{\hspace{2em}}
 \end{itemize}

\end{problem}


\begin{problem}{Factorize}
 Find the unique prime factorization of each number.

 \begin{itemize}
  \item $20$ \hfill $\underline{\hspace{2em}} \times
  \underline{\hspace{2em}} \times \underline{\hspace{2em}}$
  \item $4$ \hfill $\underline{\hspace{2em}} \times
  \underline{\hspace{2em}}$
  \item $81$ \hfill $\underline{\hspace{2em}} \times
  \underline{\hspace{2em}} \times \underline{\hspace{2em}}
  \times \underline{\hspace{2em}}$
  \item $84$ \hfill $\underline{\hspace{2em}} \times
  \underline{\hspace{2em}} \times \underline{\hspace{2em}}
  \times \underline{\hspace{2em}}$
 \end{itemize}
\end{problem}

\begin{problem}{Factors and Multiples}
 Use the word ``factor'' or ``multiple'' to complete each blank.
 
 \begin{itemize}
  \item $1$ is a \underline{\hspace{6em}} of every whole number.
  \item $0$ is a \underline{\hspace{6em}} of every whole number.
  \item $3$ is a \underline{\hspace{6em}} of $9$.
  \item All even numbers are \underline{\hspace{6em}}s of $2$.
 \end{itemize}

\end{problem}

\begin{problem}{Divisibility}
 Circle factors of each number. More than one factor may be circled.
 
 \begin{itemize}
  \item $25$ \hfill $1$~~~$2$~~~$5$~~~$10$~~~$100$
  \item $172$ \hfill $1$~~~$2$~~~$5$~~~$10$~~~$100$
  \item $1793$ \hfill $1$~~~$2$~~~$5$~~~$10$~~~$100$
  \item $2000$ \hfill $1$~~~$2$~~~$5$~~~$10$~~~$100$
 \end{itemize}
\end{problem}

\begin{problem}{Factor sum}
 The sum of all factors of $28$ is:
 
 $\underline{\hspace{2em}} + 
 \underline{\hspace{2em}} + 
 \underline{\hspace{2em}} + 
 \underline{\hspace{2em}} + 
 \underline{\hspace{2em}} + 
 \underline{\hspace{2em}} = \underline{\hspace{3em}}$
\end{problem}


\begin{problem}{Challenge}
A \emph{palindrome} is a number that reads the same forwards and backwards
in decimal notation.
For example, $12321$ is a palindrome, as is $7227$ or $888888$.

\begin{itemize}
 \item What five-digit palindrome starts with $728$? \underline{\hspace{5em}}
 \item $11$ and $55$ are two examples of two-digit palindromes.
 How many two-digit palindromes are there? ($00=0$ does not have two digits.)
 \item What two numbers are factors of all two-digit palindromes?
 \item $1221$ and $9999$ are two examples of four-digit palindromes.
 How many four-digit palindromes are there? (Do not include palindromes starting
 with $0$.)
 \item How many four-digit palindromes are even?
 \item How many four-digit palindromes are divisible by $11$?
\end{itemize}


\end{problem}



\end{document}