\documentclass[12pt,letterpaper]{article}

\newcommand{\IncludePath}{../include}
\input{\IncludePath/quiz-template.tex}

\title{Quiz 2: Parity \& Divisibility}
\author{Name: \underline{\hspace{5cm}} Mark: $\displaystyle \frac{\hspace{3em}}{50}$}
\date{March 11, 2017}

\begin{document}

\maketitle

Please write your name. It is worth one bonus mark. Problem 1 is a bonus
problem, so the maximum possible mark is 57/50. Note that this does not mean
that it is the hardest problem.

\thispagestyle{empty}

\begin{problem}{(Bonus) Factor Pairs\hfill/6}
 Complete the factor pairs.

 \begin{itemize}
  \begin{multicols}{2}
   \item $12 = 1 \times \blankB$
   \item $12 = 2 \times \blankB$
   \item $12 = 3 \times \blankB$
   \item $12 = 4 \times \blankB$
   \item $12 = 6 \times \blankB$
   \item $12 = 12 \times \blankB$
  \end{multicols}
 \end{itemize}

\end{problem}

\begin{problem}{Divisibility\hfill/20}
 Circle factors of each number. More than one factor may be circled.

 \begin{itemize}
  \item $9$ \hfill $1$~~~$2$~~~$5$~~~$10$~~~$100$
  \item $12$ \hfill $1$~~~$2$~~~$5$~~~$10$~~~$100$
  \item $40$ \hfill $1$~~~$2$~~~$5$~~~$10$~~~$100$
  \item $100$ \hfill $1$~~~$2$~~~$5$~~~$10$~~~$100$
 \end{itemize}
\end{problem}

\begin{problem}{Terminology\hfill/5}
 Use the word ``even'', ``odd'', ``factor'', or ``multiple'' to complete each
 blank. Be careful! The same word might be used more than once.

 \begin{itemize}
  \item The product of two odd numbers is \underline{\hspace{6em}}.
  \item The sum of an odd and an even number is \underline{\hspace{6em}}.
  \item $1$ is a \underline{\hspace{6em}} of every whole number.
  \item $2$ is a factor of every \underline{\hspace{6em}} number.
  \item $0$ is a \underline{\hspace{6em}} of every whole number.
 \end{itemize}

\end{problem}

\begin{problem}{Rectangle Returns\hfill/3}
 Look at the diagram below. All measurements are made in terms of small squares.

 \begin{center}
 \begin{tikzpicture}
  \draw[step=0.5] (0,0) grid (3,1.5);
 \end{tikzpicture}
 \end{center}

 \begin{enumerate}
  \item What are the dimensions of the rectangle? Don't worry about the order.
  \hfill \(\blankB\times\blankB\)
  \item Is the number of small squares even or odd? \hfill Odd \hspace{1em}
  Even
 \end{enumerate}
\end{problem}

\begin{problem}{Garden\hfill/14}
 Adam wants to grow a rectangular garden in a grid layout, with a total
 of $70$ tomatoes. List all of Adam's options for garden dimensions.
 The first one is done for you. Hint: $70=2\times5\times7$, and remember
 that factors come in pairs---if $1 \times 70 = 70$ then $70 \times 1 = 70$
 also.

 \begin{itemize}
  \begin{multicols}{2}
    \item $70 = 1 \times 70$
    \item $70 = \underline{\hspace{2em}} \times \underline{\hspace{2em}}$
    \item $70 = \underline{\hspace{2em}} \times \underline{\hspace{2em}}$
    \item $70 = \underline{\hspace{2em}} \times \underline{\hspace{2em}}$
    \item $70 = \underline{\hspace{2em}} \times \underline{\hspace{2em}}$
    \item $70 = \underline{\hspace{2em}} \times \underline{\hspace{2em}}$
    \item $70 = \underline{\hspace{2em}} \times \underline{\hspace{2em}}$
    \item $70 = \underline{\hspace{2em}} \times \underline{\hspace{2em}}$
  \end{multicols}
 \end{itemize}
\end{problem}

\begin{problem}{True or False\hfill/8}
  Circle True or False for each statement.

  \begin{itemize}
    \item If \(n\) is even, then \(4 \mid n^2\). \hfill \TFTrue
    \item If \(n\) is odd, then \(n^2 = 4m + 1\) for some integer \(m\).
    \hfill \TFTrue
    \item For all integers \(n\), \(n^3 + 3n - 1\) is odd. \hfill \TFTrue
    \item There are no integer solutions \((n, m)\) to \(n^2 = 4m + 2\).
    \hfill \TFTrue
    \item \(1234 \mid 1522755\). \hfill \TFFalse
    \item If \(4 \mid n\), then \(4n \mid (n^2+n)^2\). \hfill \TFTrue
    \item If \(m \mid n\), and \(k \mid n\), then \(m \mid n\). \hfill \TFFalse
    \item If \(3 \mid n\), but \(9 \nmid n\), then \(6 \mid n\). \hfill
    \TFFalse
  \end{itemize}
\end{problem}

\end{document}
