\documentclass[14pt,letterpaper]{article}

\newcommand{\IncludePath}{../include}
\input{\IncludePath/hmwk-template.tex}

\title{Assorted Problems I}
\author{Answers}
\date{September 24, 2016}

\begin{document}
\HomeworkTitle

\thispagestyle{empty}

\begin{problem}{A Study in Scarlet}
 A particular magnifying glass has a magnification factor of $3$. That is, if
 used to look at something that is $\SI{1}{\centi\metre}$ wide, it will appear
 to be $\SI{3}{\centi\metre}$ wide. If I use this magnifying glass to look at a
 square of side length $\SI{2}{\centi\metre}$, how large will the apparent area
 be? Give the answer in units of $\si{\centi\metre\squared}$.

 Note that this magnification factor applies to length. Since area is magnified
 in multiple dimensions, the effect of the magnifying glass will be greater on
 area than it is on length. \Ans{\SI{36}{\centi\metre\squared}}
\end{problem}

\begin{problem}{Difference of Squares}
 We can write $5^2$ to mean $5\times5$, $10^2$ to mean $10\times10$, or $777^2$
 to mean $777\times777$. In general, the notation $n^2$ stands for $n\times n$,
 where $n$ is any number.

 \begin{enumerate}[\hspace{1cm}a.]
  \item Find $100^2 - 99^2 = \Ans{199}$.
  \item Find $101^2 - 100^2 = \Ans{201}$.
 \end{enumerate}
\end{problem}

\begin{problem}{The Fourth Floor}
 An empty elevator arrives at the first floor, and some people enter. At the
 second floor, the elevator picks up $5$ people, and no people exit. At the
 third floor, half of the people in the elevator exit, and nobody enters. At the
 fourth floor, all $8$ people left on the elevator exit.

 \begin{enumerate}[\hspace{1cm}a.]
  \item How many people exited at the third floor? \Ans{8}
  \item How many people entered the elevator at the first floor? \Ans{11}
 \end{enumerate}
\end{problem}

\begin{problem}{Arranging Letters}
 There are two ways to arrange the two letters A and B into: AB and BA. Some
 ways to arrange the three letters A, B, and C include: ABC, ACB, and BCA. How
 many unique ways are there in total to arrange those three letters? (Include
 the three listed in the total. Repeating letters is not allowed.) \Ans{6}
\end{problem}

\begin{problem}{Equal Areas}
 A rectangle and a square have the same area. The rectangle's longer side (the
 length) is twice the square's side length. If the square's side length is
 \SI{20}{\centi\metre}, calculate the perimeter of the rectangle.
 \Ans{\SI{100}{\centi\metre}}
\end{problem}

\begin{problem}{Complete the Pattern}
 Figure out the pattern; then write the next two terms.

 \begin{enumerate}[\hspace{1cm}a.]
  \item 1, 1, 1, 1, \Ans{1}, \Ans{1}
  \item A, B, C, D, E, \AnsT{F}, \AnsT{G}
  \item 2, 4, 6, 8, \Ans{10}, \Ans{12}
  \item 3, 9, 27, 81, \Ans{243}, \Ans{729}
  \item $\uparrow$, $\leftarrow$, $\downarrow$, $\rightarrow$, $\uparrow$,
  $\leftarrow$, \Ans{\downarrow}, \Ans{\rightarrow}
  \item O, T, T, F, F, S, S, E, \AnsT{N}, \AnsT{T}
  \item 1, 2, 6, 24, 120, 720, \Ans{5040}, \Ans{40320}
  \item 0, 1, 1, 2, 3, 5, 8, 13, 21, \Ans{34}, \Ans{55}
 \end{enumerate}
\end{problem}

\end{document}
