\documentclass[12pt,letterpaper]{article}

\usepackage{tikz}
\usetikzlibrary{shapes}

\usepackage{amssymb,amsmath,amsthm}
\usepackage{enumerate}
\usepackage[margin=1.25in]{geometry}
\usepackage{graphicx,ctable,booktabs}
\usepackage{fancyhdr}
\usepackage[utf8]{inputenc}
\usepackage{gensymb}
\usepackage{wrapfig}

\makeatletter
\newenvironment{problem}{\@startsection
       {section}
       {1}
       {-.2em}
       {-3.5ex plus -1ex minus -.2ex}
       {2.3ex plus .2ex}
       {\pagebreak[3]
       \large\bf\noindent{Problem }
       }
       }
\makeatother

\title{Angles of a Polygon}
\author{Name: \underline{\hspace{5cm}}}
\date{October 17, 2015}

\pagestyle{fancy}
\lhead{Angles of a Polygon}
\chead{} 
\rhead{\thepage} 
\lfoot{\small\scshape Grade 4 Olympic Math} 
\cfoot{} 
\rfoot{}
\renewcommand{\headrulewidth}{.3pt} 
\renewcommand{\footrulewidth}{.3pt}
\setlength\voffset{-0.25in}
\setlength\textheight{648pt}
\setlength\headheight{15pt}

\begin{document}

\maketitle

\thispagestyle{empty}

\begin{problem}{Angle sum of a triangle}
 Could each of the following triplets form the angles of a
 valid triangle?

 \begin{itemize}
  \item $110\degree$, $36\degree$, $8\degree$
  \hfill Yes~~No
  \item $100\degree$, $53\degree$, $27\degree$
  \hfill Yes~~No
  \item $108\degree$, $16\degree$, $150\degree$
  \hfill Yes~~No
 \end{itemize}
\end{problem}

\begin{problem}{Possible?}
 For each of the following statements, indicate whether the
 statement is possible or otherwise.
 
 \begin{itemize}
  \item A triangle has two obtuse angles.
  \hfill Possible~~Not Possible
  \item A triangle has three acute angles.
  \hfill Possible~~Not Possible
 \end{itemize}
\end{problem}

\begin{problem}{The missing angle 1}
 Find the missing angle in each triangle angle triplet.
 
 \begin{itemize}
  \item $85\degree$, $85\degree$,
  $\underline{\hspace{3em}}\degree$
  \item $30\degree$, $60\degree$,
  $\underline{\hspace{3em}}\degree$
  \item $90\degree$, $45\degree$,
  $\underline{\hspace{3em}}\degree$
 \end{itemize}
\end{problem}

\begin{problem}{Angle sum of a polygon}
 What is the sum of the interior angles of each following
 polygon?
 
 \begin{itemize}
  \item Hexagon ($6$-sided)
  \hfill Sum: $\underline{\hspace{3em}}\degree$
  \item Hendecagon ($11$-sided)
  \hfill Sum: $\underline{\hspace{3em}}\degree$
 \end{itemize}
\end{problem}

\begin{problem}{Hexagon}
 Can five of the angles in a hexagon measure
 $30\degree$, $40\degree$, $50\degree$, $60\degree$, and
 $70\degree$?
\end{problem}

\begin{problem}{Challenge}
 A \emph{convex} polygon has no reflex angles; that is, all
 angles of a convex polygon are less than $180\degree$.
 Answer the below in the space provided.
 
 \begin{itemize}
  \item $20\degree$, $50\degree$, and $110\degree$ are the
  three interior angles of a convex triangle. What is the
  sum of the exterior angles of this triangle?
  \item Pick three other angles that add up to $180\degree$
  and find the sum of exterior angles of the triangle that
  contains those angles. What do you notice?
  \item What is the sum of the exterior angles of a convex
  polygon? Hint: Pick $5$ angles that sum to $540\degree$.
  Calculate the exterior angles and add those up.
  \item What is true about the sum of exterior angles of
  any polygon? Why do you think this is the case?
 \end{itemize}

\end{problem}


\end{document}