%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%This is a science homework template. Modify the preamble to suit your needs. 
%The junk text is   there for you to immediately see how the headers/footers look at first 
%typesetting.


\documentclass[14pt,letterpaper]{article}

\usepackage{extsizes}

%AMS-TeX packages
\usepackage{amssymb,amsmath,amsthm}
\usepackage{enumerate}
%geometry (sets margin) and other useful packages
\usepackage[margin=1.25in]{geometry}
\usepackage{graphicx,ctable,booktabs}


%
%Redefining sections as problems
%
\makeatletter
\newenvironment{problem}{\@startsection
       {section}
       {1}
       {-.2em}
       {-3.5ex plus -1ex minus -.2ex}
       {2.3ex plus .2ex}
       {\pagebreak[3]%forces pagebreak when space is small; use \eject for better results
       \large\bf\noindent{Problem }
       }
       }
       %{%\vspace{1ex}\begin{center} \rule{0.3\linewidth}{.3pt}\end{center}}
       %\begin{center}\large\bf \ldots\ldots\ldots\end{center}}
\makeatother


%
%Fancy-header package to modify header/page numbering 
%
\usepackage{fancyhdr}

\title{Introduction to Contest Math}
\author{Name: \underline{\hspace{5cm}}}
\date{September 26, 2015}

\usepackage[utf8]{inputenc}

\pagestyle{fancy}
%\addtolength{\headwidth}{\marginparsep} %these change header-rule width
%\addtolength{\headwidth}{\marginparwidth}
\lhead{Introduction to Contest Math}
\chead{} 
\rhead{\thepage} 
\lfoot{\small\scshape Grade 4 Olympic Math} 
\cfoot{} 
\rfoot{} 
\renewcommand{\headrulewidth}{.3pt} 
\renewcommand{\footrulewidth}{.3pt}
\setlength\voffset{-0.25in}
\setlength\textheight{648pt}
\setlength\headheight{15pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%
%Contents of problem set
%    
\begin{document}



\maketitle

\thispagestyle{empty}

%Example problems
\begin{problem}{Arranging Letters}
ABC, ACB, and BCA are three ways to arrange the three letters ABC. How
many unique ways are there in total? (Include the three listed
in the total; repeating letters is not allowed.)
\end{problem}

\begin{problem}{Equal Areas}
A rectangle and a square have the same area. The rectangle's longer side (the
length) is twice the square's side length. If the square's side length is $20~\mathrm{cm}$,
calculate the perimeter of the rectangle.
\end{problem}

\begin{problem}{Handshakes}
 Four people attend a meeting. Each shakes the hand of every person
 (except themselves) exactly once. How many handshakes occur?
\end{problem}

\begin{problem}{Guess the Number}
 A number yields a remainder of 1 when divided by 2, a remainder of 2
 when divided by 3, a remainder of 3 when divided by 4, and a remainder of 4 when divided by
 5.

 \begin{enumerate}[\hspace{1cm}a.]
  \item What is the smallest positive number to have this property?
  \item Give two other positive numbers to have the above property.
 \end{enumerate}
\end{problem}

\begin{problem}{Garden}
 The area of a rectangular garden is $36~\mathrm{m^2}$. What are its dimensions if\ldots
 
 \begin{enumerate}[\hspace{1cm}a.]
   \item \ldots{}the width is $3~\mathrm{m}$?
   \item \ldots{}the length and width are equal?
   \item \ldots{}the perimeter is $26~\mathrm{m}$?
 \end{enumerate}
\end{problem}

\begin{problem}{Challenge}
 Write the next two terms in each pattern.

 \begin{enumerate}[\hspace{1cm}a.]
  \item 1, 1, 1, 1\ldots
  \item A, B, C, D, E\ldots
  \item 2, 4, 6, 8\ldots
  \item 3, 9, 27, 81\ldots
  \item $\uparrow$, $\leftarrow$, $\downarrow$, $\rightarrow$, $\uparrow$, $\leftarrow$ \ldots
  \item O, T, T, F, F, S, S, E\ldots
  \item 1, 2, 6, 24, 120, 720\ldots
  \item 0, 1, 1, 2, 3, 5, 8, 13, 21\ldots
 \end{enumerate}

\end{problem}

\end{document}