\documentclass[12pt,letterpaper]{article}

\newcommand{\IncludePath}{../include}
\input{\IncludePath/quiz-template.tex}

\title{Fractions \& Probability Quiz}
\author{Name: \underline{\hspace{5cm}} Mark: $\displaystyle \frac{\hspace{3em}}{4}$}

\begin{document}

\maketitle

\thispagestyle{empty}

Do \textbf{six} of the eight problems below. (You can choose which six problems
to do.) When you're done, please hand in the quiz and start the investigation.

\begin{problem}{Equivalent Fractions}
 Find the equivalent fraction with the smallest denominator. (In other words,
 simplify the fraction as much as possible.)

 \begin{enumerate}[\hspace{.5cm}a.]
  \item $\frac{3}{6}$
  \item $\frac{4}{12}$
 \end{enumerate}
\end{problem}

\begin{problem}{Adding and Multiplying Fractions}
Find the sum or product:

\begin{enumerate}[\hspace{.5cm}a.]
\item $\frac{1}{3} + \frac{1}{3}$
\item $\frac{1}{3} \times \frac{1}{2}$
\end{enumerate}
\end{problem}

\begin{problem}{Simple Probability}
\begin{enumerate}[\hspace{.5cm}a.]
\item I roll a fair six-sided die $D_6$. What's the probability that I roll a
$5$?
\item I have a bag with $2$ green marbles, $3$ blue marbles, and $4$ red
marbles. I pick a marble at random. What's the probability that I pick a red
marble?
\end{enumerate}
\end{problem}

\begin{problem}{Compound Probability}
\begin{enumerate}[\hspace{.5cm}a.]
\item I flip a fair coin twice. What's the probability both flips show heads?
\item I roll a fair four-sided die twice. What's the probability that the
numbers shown add up to $2$?
\end{enumerate}
\end{problem}

\end{document}
