%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%This is a science homework template. Modify the preamble to suit your needs. 
%The junk text is   there for you to immediately see how the headers/footers look at first 
%typesetting.


\documentclass[12pt,letterpaper]{article}

\usepackage{extsizes}

%AMS-TeX packages
\usepackage{amssymb,amsmath,amsthm}
\usepackage{enumerate}
%geometry (sets margin) and other useful packages
\usepackage[margin=1.25in]{geometry}
\usepackage{graphicx,ctable,booktabs}


%
%Redefining sections as problems
%
\makeatletter
\newenvironment{problem}{\@startsection
       {section}
       {1}
       {-.2em}
       {-3.5ex plus -1ex minus -.2ex}
       {2.3ex plus .2ex}
       {\pagebreak[3]%forces pagebreak when space is small; use \eject for better results
       \large\bf\noindent{Problem }
       }
       }
       %{%\vspace{1ex}\begin{center} \rule{0.3\linewidth}{.3pt}\end{center}}
       %\begin{center}\large\bf \ldots\ldots\ldots\end{center}}
\makeatother


%
%Fancy-header package to modify header/page numbering 
%
\usepackage{fancyhdr}

\title{Logical Reasoning}
\author{Name: \underline{\hspace{5cm}}}
\date{September 27, 2014}

\usepackage[utf8]{inputenc}

\pagestyle{fancy}
%\addtolength{\headwidth}{\marginparsep} %these change header-rule width
%\addtolength{\headwidth}{\marginparwidth}
\lhead{Logical Reasoning}
\chead{} 
\rhead{\thepage} 
\lfoot{\small\scshape Grade 4 Olympic Math} 
\cfoot{} 
\rfoot{} 
\renewcommand{\headrulewidth}{.3pt} 
\renewcommand{\footrulewidth}{.3pt}
\setlength\voffset{-0.25in}
\setlength\textheight{648pt}
\setlength\headheight{15pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%
%Contents of problem set
%    
\begin{document}

\maketitle

\thispagestyle{empty}

%Example problems
\begin{problem}{Cold Snow}
If it is snowing, then it is cold. Which of the below statements is a logical conclusion?

\begin{enumerate}[\hspace{.5cm}a.]
\item If it is cold, then it is snowing.
\item If it is not cold, then it is not snowing.
\item If it is not snowing, then it is not cold.
\end{enumerate}
\end{problem}

\begin{problem}{Logical Weather}
Select the statements where the left side logically implies the right side.

\begin{enumerate}[\hspace{.5cm}a.]
\item It is raining and it is cloudy $\to$ It is cloudy.
\item It is sunny or it is snowing. $\to$ It is snowing or it is sunny.
\item It is cold or it is not foggy. $\to$ It is foggy and it is cold.
\item It is not hot and it is not humid. $\to$ It is hot or it is humid.
\end{enumerate}
\end{problem}

\begin{problem}{Alvin in the Rain}
 If it is not raining, then Alvin is happy. Which of the following statements is a logical conclusion?
 
 \begin{enumerate}[\hspace{.5cm}a.]
  \item It is not raining and Alvin is happy.
  \item It is raining or Alvin is happy.
  \item If Alvin is happy, then it is not raining.
 \end{enumerate}
\end{problem}

\begin{problem}{Treasure Chest}
The key to a treasure chest is hidden in one of box A, box B, or box C.
It is either yellow, blue, or green. Where is the key given the
following statements? Is it possible to logically determine the colour
of the key, or is there not enough information to determine that?

 \begin{enumerate}
  \item If the key is in box C, then the key is yellow.
  \item If the key is blue, then the key is not in box B.
  \item If the key is not green, then the key is in box A.
  \item If the key is not in box C, then the key is not green.
 \end{enumerate}
\end{problem}

\begin{problem}{Inconclusive}
 Identify the statements that are not logical conclusions. (Assume the
 left hand side is true.) That is, the left side alone does not logically
 imply the right side.
 
 \begin{enumerate}[\hspace{.5cm}a.]
  \item If it is cold and it is snowing, then it is winter. It is winter. $\to$ Either it is cold or it is snowing, or both.
  \item If the sun shines at 7:00, then it is summer. It is not summer. $\to$ The sun is not shining at 7:00.
  \item All birds are animals. Some animals are mammals. $\to$ Some birds are mammals.
  \item All frogs eat flies. Some frogs eat mosquitoes. $\to$ Some frogs eat both mosquitoes and flies.
 \end{enumerate}

\end{problem}


\begin{problem}{Challenge}
You find three treasure boxes. Only one of them has treasure;
the other two have nothing. Each treasure box has a message written
on it. Only one of these messages is true; the other two are false.
Which treasure box has the treasure?

\begin{enumerate}
\item The treasure is not here.
\item The treasure is not here.
\item The treasure is in box 2.
\end{enumerate}
\end{problem}

\end{document}