\documentclass[12pt,letterpaper]{article}

\newcommand{\IncludePath}{../include}
\input{\IncludePath/hmwk-template.tex}

\title{Events \& Expected Value}
\author{Name: \underline{\hspace{5cm}}}
\date{October 4, 2014}

\begin{document}

\maketitle

\thispagestyle{empty}

\begin{problem}{Independent Events}
 Select the pairs of events that are independent. Remember that events are
 independent if the outcome of one does not affect the other.

 \begin{enumerate}[\hspace{.5cm}a.]
  \item I draw a card from a deck of cards. Then I draw another card from the
  same deck, without replacement.
  \item I roll a four-sided die. Then I roll a six-sided die.
  \item I have a bag of red and blue balls. I draw a ball, then put it back into
  the bag. Then I draw another ball.
 \end{enumerate}
\end{problem}

\begin{problem}{Joint Probability}
I roll a four-sided die $D_4$, then a six-sided die $D_6$, and then flip a coin
$C$. All are fair. Find the probability of:

\begin{enumerate}[\hspace{.5cm}a.]
\item $D_4$ is even and $C$ shows heads.
\item $D_4=2$, $D_6=6$, and $C$ shows tails.
\item $D_4 + D_6 = 10$
\end{enumerate}
\end{problem}

\begin{problem}{Coin Flips}
A fair coin is flipped $5$ times. What's the probability that they're all heads?
\end{problem}

\begin{problem}{Marbles}
A bag contains $2$ blue marbles and $3$ red marbles. I take a marble out of the
bag at random, then put it back in. I do this until I have taken out (and
returned) $3$ marbles. What's the probability that they're all red?
\end{problem}

\begin{problem}{The Sum Rule}
 I roll a fair 4-sided die and a fair 6-sided die. What's the probability that I
 will see a $3$ on one die, and any odd number on the other? (It doesn't matter
 which die shows the odd number and which shows the $3$.)

 To solve the question, you need to use the sum rule:

 \begin{equation*}
  \underbrace{P(A \cup B)}_\text{A or B happens}
  = \underbrace{P(A)}_\text{A happens} + \underbrace{P(B) -
  P(A \cap B)}_\text{B happens but A does not}
 \end{equation*}

 To calculate the probability of $A$ or $B$ happening, we can add the cases that
 $A$ happens, and the cases where $B$ happens but $A$ doesn't also happen. (We
 can't just add $P(A)$ and $P(B)$ because then we'd be double-counting the cases
 where both $A$ and $B$ happen!)
\end{problem}

\begin{problem}{Dependent Events}

 A bag contains $2$ blue marbles and $3$ red marbles. Two marbles are drawn from
 the bag, without replacing marbles after they are drawn. Find the probability
 that:

 \begin{enumerate}[\hspace{.5cm}a.]
  \item Both marbles are red.
  \item Both marbles are blue.
  \item One marble is red and one marble is blue. (The order of marbles does not
  matter.)
 \end{enumerate}

 \emph{Careful---since we aren't replacing marbles, the colours of the two
 marbles are not independent!}
\end{problem}

\begin{problem}{Challenge}
 If I roll a fair six-sided die $4$ times, what's the probability that at least
 one will show $6$?
\end{problem}

\begin{problem}{Expected Value}
Calculate the expected value (optional):

 \begin{enumerate}[\hspace{.5cm}a.]
  \item If I roll a six-sided die ($1$ to $6$).
  \item If I roll a six-sided die, but the face with $6$ is edited to $9$.
  \item If I roll $8$ six-sided dice and add the results.
 \end{enumerate}
\end{problem}

\end{document}
