\documentclass[12pt,letterpaper]{article}

\usepackage{extsizes}

\usepackage{amssymb,amsmath,amsthm}
\usepackage{enumerate}
\usepackage[margin=1.25in]{geometry}
\usepackage{graphicx,ctable,booktabs}
\usepackage{fancyhdr}
\usepackage[utf8]{inputenc}

\makeatletter
\newenvironment{problem}{\@startsection
       {section}
       {1}
       {-.2em}
       {-3.5ex plus -1ex minus -.2ex}
       {2.3ex plus .2ex}
       {\pagebreak[3]
       \large\bf\noindent{Problem }
       }
       }
\makeatother

\title{Fractions \& Probability Quiz}
\author{Name: \underline{\hspace{5cm}}}
\date{November 1, 2014}

\pagestyle{fancy}
\lhead{Fractions \& Probability Quiz}
\chead{} 
\rhead{\thepage} 
\lfoot{\small\scshape Grade 4 Olympic Math} 
\cfoot{} 
\rfoot{} 
\renewcommand{\headrulewidth}{.3pt} 
\renewcommand{\footrulewidth}{.3pt}
\setlength\voffset{-0.25in}
\setlength\textheight{648pt}
\setlength\headheight{15pt}

\begin{document}

\maketitle

\thispagestyle{empty}

Do \textbf{six} of the eight problems below. (You can choose which six problems to do.)
When you're done, please hand in the quiz and start the investigation.

\begin{problem}{Equivalent Fractions}
 Find the equivalent fraction with the smallest denominator. (In other words, simplify the fraction as much as possible.)
 
\begin{enumerate}[\hspace{.5cm}a.]
\item $\frac{3}{6}$
\item $\frac{4}{12}$
\end{enumerate}
\end{problem}

\begin{problem}{Adding and Multiplying Fractions}
Find the sum or product:

\begin{enumerate}[\hspace{.5cm}a.]
\item $\frac{1}{3} + \frac{1}{3}$
\item $\frac{1}{3} \times \frac{1}{2}$
\end{enumerate}
\end{problem}

\begin{problem}{Simple Probability}
\begin{enumerate}[\hspace{.5cm}a.]
\item I roll a fair six-sided die $D_6$. What's the probability that I roll a $5$?
\item I have a bag with $2$ green marbles, $3$ blue marbles, and $4$ red marbles.
I pick a marble at random. What's the probability that I pick a red marble?
\end{enumerate}
\end{problem}

\begin{problem}{Compound Probability}
\begin{enumerate}[\hspace{.5cm}a.]
\item I flip a fair coin twice. What's the probability both flips show heads?
\item I roll a fair four-sided die twice. What's the probability that the numbers shown add up to $2$?
\end{enumerate}
\end{problem}

\end{document}